The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
fixed equation 5
explained gauss CRP algorithm

		The value of the first DIT can be found by solving the following modular
		equation system:

		%TODO : change format so that the equation number is displayed correctly

		\begin{equation}
			t_d = \min
			\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
				\left\{
					\begin{array}{c}
						t > 0 \\
						t \equiv a_i \; (mod \; T_i) \\
					\end{array}
				\right.
			\right)
		\end{equation}
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones}.

@@

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A better method for finding the
		FPDIT consists in splitting Gauss's algorithm into two separate parts, as
		shown in Algorithm~\ref{alg:multiACRP} (note that $x^{-1} \; (mod \; y)$
		means the modular inverse of $x$ in the naturals modulo $y$).

@@

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall i: A_i$ is the set of possible $a_i$ values for
					task $\tau_i$
				\REQUIRE $H$ is the hyperperiod of the system

@@

		The global structure of the original algorithm is simply a sum of factors, each term being dependent on which $a_i$ value is chosen. A major
		speedup is achieved by first computing all possible terms for each task
		then creating all possible DIT values by summing the terms in all possible
		ways. The number of results is still exponential in the number of tasks, but
		the only operation that is repeated exponentially many times is now a sum.
		This allows us to profit from a high chance of having DITs when the deadlines
		are close to the WCETs (and far from the periods), but with only a slight
		increase in computation time as the sizes of the $[D_i, T_i]$ intervals grow.

>>>>

		The value of the first DIT can be found by solving the following modular
		equation system:	
		\begin{equation}
			\begin{split}
				 t_d = \min(& \{ t \; s.t. \; t > 0 \; and \\ 
						& \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]: t \equiv a_i \;
						(mod \; T_i) \})
			\end{split}
		\end{equation}
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

	\subsection{Solving the modular system}
		The existence conditions of	Section~\ref{sct:FPDITexist} can directly be used to calculate the value of
		the FPDIT (if any), because for a given set of $a_i$ values the problem of
		finding the corresponding DIT is an instance of the Chinese Remainder Problem
		(CRP), which is easily solved using Gauss's CRP solving method for non-coprime
		moduli \cite{gauss1965disquisitiones}. (note that $x^{-1} \; (mod \; y)$
		means the modular inverse of $x$ in the naturals modulo $y$)

		\begin{algorithm}
			\caption{Gauss's CRP Algorithm}
			\label{alg:algoCRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall \tau_i \in \tau : a_i \in [D_i,T_i]$
				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
				$n_i$ become pairwise coprime

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} (mod \; n_i)$
					\STATE $e_i \leftarrow (Mj \cdot invMj)$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{a_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}

@@

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks, and resolving
		exponentially many CRP is prohibitively slow. A faster method for finding
		the FPDIT consists in merging all these CRP instances into one problem
		(finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the needed
		intermediate results are shared between instances.

@@

		\begin{algorithm}
			\caption{Modified Gauss Algorithm}
			\label{alg:multiACRP}
			\begin{algorithmic}[1]
				\REQUIRE $\forall \tau_i \in \tau: A_i$ is the set of possible $a_i$ values
				for $\tau_i$
				\REQUIRE $\forall \tau_i \in \tau : n_i = T_i$
				\REQUIRE $H$ is the hyperperiod of the system

				\STATE Modify the $n_i$ and $a_i$ by prime decomposition so \\ that the
				$n_i$ become pairwise coprime

@@

		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
		computation of one modular inversion per $a_i$ value, which is done in linear
		time with the number of tasks. However, to find all DITs
		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
		combination of $a_i$ values, which is exponential in the number of tasks.
		Algorithm~\ref{alg:multiACRP} is not faster in orders of
		complexity as the computation of all DITs still requires an exponential number
		of answers in the number of tasks, but it is nonetheless significantly faster
		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
		sensitive to the number of different $a_i$ values per task, which means tasks
		with deadlines significantly smaller than periods remain practical.
